\documentclass[11pt]{letter}
\usepackage[margin=2.5cm]{geometry}
\usepackage{hyperref}

\signature{Yongjun Kim\\College of Software Convergence\\Ajou University\\Suwon, South Korea\\yjkim0123@ajou.ac.kr}

\begin{document}

\begin{letter}{Editor-in-Chief\\Pacific-Basin Finance Journal}

\opening{Dear Editor,}

I am pleased to submit our manuscript entitled \textbf{``Pre-Disclosure Price Discovery in Korean Earnings Announcements: Evidence of Information Leakage Under Fair Disclosure Regulation''} for consideration for publication in the \textit{Pacific-Basin Finance Journal}.

This study examines the effectiveness of South Korea's Fair Disclosure regulation by analyzing 2,221 earnings disclosure filings from 64 major KOSPI-listed companies across 12 chaebol groups between 2020 and 2026. Our key finding is that 91\% of cumulative abnormal returns in the [-5,+5] event window accumulate \textit{before} the official DART filing date, accompanied by statistically significant abnormal trading volume beginning three days prior to disclosure. This suggests that either the Fair Disclosure regime is insufficient to prevent selective information leakage, or that Korea's earnings disclosures are highly predictable to sophisticated investors.

We believe this manuscript is a strong fit for PBFJ for several reasons:
\begin{itemize}
    \item It provides timely evidence on the long-term effectiveness of a major Pacific-Basin securities regulation using the most recent data (2020--2026).
    \item It documents a previously unreported structural shift in pre-announcement drift, from positive during 2020--2022 to negative in 2024--2026.
    \item It leverages the comprehensive DART electronic filing system, which is a unique institutional feature of the Korean market.
    \item The findings have direct policy implications for the Korean Financial Supervisory Service and other Pacific-Basin regulators considering fair disclosure reforms.
\end{itemize}

The manuscript has not been previously published, is not under consideration elsewhere, and all data sources are publicly available. Analysis code is available at \url{https://github.com/yjkim0123/pre-disclosure-leakage}.

Thank you for considering this submission. I look forward to hearing from you.

\closing{Sincerely,}

\end{letter}
\end{document}
